\documentclass[12pt,letterpaper]{article}

\input{preamble}

\begin{document}\thispagestyle{empty}\sloppy\sloppypar

% Name and contact, website, etc.
{\huge \name}
\vspace{-0.25em}

\begin{itemize}
	\item The Cosmic Dawn Center, Niels Bohr Institute, University of Copenhagen
	\item  ORCID ID: \href{https://orcid.org/0000-0001-9058-3892}{0000-0001-9058-3892}
	\item Email: \href{mailto:jselsing@nbi.ku.dk}{jselsing@nbi.ku.dk} 
	\item Personal website: \href{http://astroman.io}{astroman.io} 
	%  --- \href{http://somename.nn}{http://somename.nn}
\end{itemize}



\section*{Personal data}

\begin{itemize}
	\item Nationality: Danish
	\item Spouse: Malene Selsing Mouritzen
	\item Child: Marie Selsing (b. 2016) 
	\item Paternity leave: Jan. - Jul. 2017
	
\end{itemize}


\section*{Employment}
\begin{itemize}
	\item Postdoctoral researcher, The Cosmic Dawn Center, Niels Bohr Institute, University of Copenhagen.  2018 --
\end{itemize}


\section*{Education}
	\begin{itemize}
	\item PhD 2018, Astronomy, Dark Cosmology Centre, University of Copenhagen.
		{Advisor: L. Christensen}
	\item MA 2015, Physics, University of Copenhagen.
		{Advisor: L. Christensen}
	\item BA 2011, Physics, University of Copenhagen.
		{Advisor: J. Hjorth}
	\end{itemize}


\section*{Core scientific research  fields}

\begin{itemize}
	\item Kilonovae, Supernovae, Gamma-Ray Bursts, Tidal Disruption Events, Quasars
\end{itemize}


\section*{International collaboration memberships}

\begin{itemize}
	\item Electromagnetic counterparts of gravitational wave sources at the Very Large Telescope (\href{http://www.engrave-eso.org}{ENGRAVE}), Swift response Transient Astrophysics Research (STARGATE), X-Shooter Gamma-Ray Burst collaboration (XSGRB)
\end{itemize}


\section*{Awards}

	\begin{itemize}
    \item Jens Martin prize, awarded for excellence in teaching (2015)
	\end{itemize}

%\newpage
%\input{publications}
%\newpage

\section*{Approved observing proposals}

	\begin{itemize}
    \item {\it Piercing dark lenses with highly magnified transients}, ESO/VLT X-shooter,  099.A-0801(A)
    \item {\it Exploiting the extreme magnification of a caustic-crossing event. Imaging a single star at z = 1.49.}, ESO/VLT FORS,  297.A-5026(A)
    \item {\it The wonders of gravitational lensing: Imaging a single star at z = 1.5.}, NOT ALFOSC,  53-407
	\end{itemize}

\section*{Observing experience}

\begin{itemize}
	\item NOAO, Cerro Tololo, Blanco 4m, Cluster weak lensing observations with DECam over 5 half-nights(PI: Anja von der Linden, KIPAC)
	\item Roque de los Muchachos, NOT 2.5m, ALFOSC for variability studies over 2 full nights(PI: Johan Fynbo, DARK).
\end{itemize}


\section*{Scientific Talks}

\begin{itemize}
	\item \emph{The X-shooter sample of GRB afterglows (XSGRB)}, EWASS, Liverpool, 2018
	\item \emph{The spectroscopic evolution of AT2017gfo as seen by VLT/X-shooter and the implications for kilonova models.}, EWASS, Liverpool, 2018
    \item \emph{The X-shooter GRB afterglow sample}, XSGRB workshop, Meudon Observatory - Observatoire de Paris, 2016
    \item \emph{The XSGRB sample}, DARK cake talks, Dark Cosmology Centre, 2016
    \item \emph{A composite spectrum of GRB afterglows}, IMPS takes Esalen, California, 2016 
    \item \emph{Lessons from a bright quasar composite}, Department lunch talks, UC Berkeley, 2016 
    \item \emph{The last rise of Refsdal}, IMPS talk, UC Santa Cruz, 2015
    \item \emph{Quasar composite from UV to near-infrared}, IMPS talk, UC Santa Cruz, 2015
    \item \emph{Local environments of SNe Ic and Ic-BL}, XXIX IAU General Assembly, Hawaii, 2015.
    \item \emph{Composite spectrum of the afterglow sample}, XSGRB workshop, IAA-CSIC Granada, 2014
    \item \emph{IFS of Ic-BL SNe}, Galaxies meet GRBs, Cabo de Gata, 2013


\end{itemize}


\section*{Open source development (\href{https://github.com/jselsing}{GitHub profile})}


\section*{Teaching}

\begin{itemize}
	
	\item \emph{Introductory Cosmology}, TA, 2013, University of Copenhagen
    \item \emph{Introductory Classical Mechanics}, TA, 2013, University of Copenhagen
	\item \emph{Advanced Classical Mechanics}, TA, 2013, University of Copenhagen
\end{itemize}


\section*{Public outreach}

\begin{itemize}
	\item \emph{Gravitational waves, Kilonovae and the history of gold.}, 2018, public outreach talk, Rysensteen Gymnasium, DK
	\item \emph{Gravitational waves, Kilonovae and the history of gold.}, 2018, public outreach talk, naNODE, DTU, DK
    \item \emph{Science breakthrough of the year 2017 (\AA rets videnskabelige gennembrud)}, 2018, DR2 Dagen - national danish television, DK	
    \item \emph{Gravitational Waves and their EM counterparts}, 2017, public outreach talk, Brorfelde observatory, DK
    \item \emph{Gravitational waves, Kilonovae and the history of gold.}, 2017, Danish society of engineers, IDA, DK
    \item \emph{Gravitational waves, Kilonovae and lots of gold.}, 2017, motivational day for interested elementary school students, University of Copenhagen, DK
    \item \emph{Gravitational waves, Kilonovae and the origin of gold.}, 2017, theme day for high-school teachers, University of Copenhagen, DK
    \item \emph{Gravitational waves from a neutron star merger}, 2017, high school motivational talk, University of Copenhagen, DK
    \item \emph{GW170817/GRB170817A}, 2017, Appeared on danish national television and in most major newspapers, cited in 52 individual articles on the observations of GW170817/GRB170817A, DK    
    \item \emph{GRBs and Supernovae}, 2016, public outreach talk, NOVA astronomical society, Helsingor, DK
    \item \emph{Astronomy; how to be cool}, 2016, motivational talk for young students, University of Copenhagen, DK
    
    \item Guide, 2010-2012, Tycho Brahe Planetarium, DK

\end{itemize}

\end{document}
